---
output:
  github_document:
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures",
  fig.width = 10,
  asciicast_theme = if (Sys.getenv("IN_PKGDOWN") == "true") "pkgdown" else "readme"
)
asciicast::init_knitr_engine(
  echo = TRUE,
  echo_input = FALSE,
  startup = quote({
    library(cli)
    options(cli.num_colors = cli::truecolor)
  })
)
```

# tsitter

<!-- badges: start -->
![lifecycle](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg)
[![R-CMD-check](https://github.com/r-lib/tsitter/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/tsitter/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Common tree-sitter parsing tools for R.

tsitter is a common interface to [tree-sitter](
  https://tree-sitter.github.io/tree-sitter/) parsers, implemented in
other R packages. It has a common API to

- query,
- edit,
- format, and
- unserialize

tree-sitter parse trees.

## Installation

Install tsitter from CRAN:

```{r, eval = FALSE}
install.packages("tsitter")
```

## Documentation

See at [`https://r-lib.github.io/tsitter/`](
  https://r-lib.github.io/tsitter/reference/index.html)
and also in the installed package: `help(package = "tsitter")`.

## Parsers that use tsitter

- JSONC (JSON with comments and trailing commas): [tsjsonc](
  https://gaborcsardi.github.io/tsjsonc/).
- TOML: [tstoml](https://gaborcsardi.github.io/tstoml/).

## Quickstart

```{r include = FALSE}
file.copy("tools/man/about.Rmd", ".")
```

```{r child ="about.Rmd"}
```

```{r include = FALSE}
unlink("about.Rmd")
```

# License

MIT © Posit Software, PBC
